\emph{hp}-Finite Element Model of Poisson and Nernst-Planck\\ System of Equations

### 2010-10-11 pugal-esco2010.tex
Minor changes (address etc).

\title{\emph{hp}-Finite Element Model of Poisson and Nernst-Planck System of Equations}

@@

\address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
\address[unrmath]{FEM group, Department of Mathematics and Statistics,\\
University of Nevada, Reno, NV, U.S.A.}
\address[czech]{Institute of Thermomechanics, Prague, Czech Republic}
\address[tartu]{Institute of Technology, Tartu University, Estonia}

\cortext[cor1]{Corresponding author}
\cortext[cor2]{Principal correpsonding auhtor}

>>>>

\title{\emph{hp}-Finite Element Model of Poisson and Nernst-Planck\\ System of Equations}

@@

\address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
\address[unrmath]{Department of Mathematics and Statistics,
University of Nevada, Reno, NV, U.S.A.}
\address[czech]{Institute of Thermomechanics, Prague, Czech Republic}
\address[tartu]{Institute of Technology, Tartu University, Estonia}

\cortext[cor1]{Corresponding author}
\cortext[cor2]{Principal corresponding author}
